Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Respond to review concerning perfectly known environments.

Simplifying  the environment  consists in  considering obstacles  at a
footstep   level only.   \cite{kuffner2001footstep,chestnutt2005footstep,kuffner2005motion}
use   an  A$^{*}$   algorithm  to   find
collision-free   footsteps.    In   \cite{perrin2012fast},   the   authors   compute
dynamic walking motions avoiding collisions at the leg level
by using  an RRT algorithm.

>>>>

\textbf{One possible simplification of the environment consists in
  considering obstacles at a footstep level only.
  \cite{kuffner2001footstep,chestnutt2005footstep,kuffner2005motion}
  use an A$^{*}$ algorithm to find collision-free footsteps.}  In
\cite{perrin2012fast}, the authors compute dynamic walking motions
avoiding collisions at the leg level by using an RRT algorithm.
